Appeal of rejection of GCB-20-1713

### 2020-09-18 manuscript/journal_submissions/2020_8_GCB/appeal.Rmd
integrated references

**(1) Reviewer 1 provided an inaccurate assessment of the scope of our analysis relative to previous studies.**  The reviewer states, "...the findings seem not improving contemporary knowledge of forest carbon cycling, and the study appears to be a simple statistical analyses of literature data..." and "the analyses performed were too conventional that similar analyses with a smaller size of similar datasets have been performed a decade ago." These statements betray a lack of perspective on the scope of our analysis relative to previous studies. Whereas most studies consider at most a few flux variables, our considers nine. The most comprehensive similar study is @luyssaert_co_2007, which was published in *GCB* more than a decade ago, includes much less data, does not control for effects of stand age/ disturbance history, and examines latitudinal/ global climatic trends in only 3 variables. This study has been cited >580 times and was highlighted as a noteworthy publication within *GCB* ([Long, 2020](https://doi.org/10.1111/gcb.14921)). It would seem that something along these lines, but with an expanded database and a more carefully controlled treatment of forest age and management/disturbance history, would have high potential to become a "classic" reference in global forest carbon cycling.

@@

**(3) Reviewer 1 set an unrealistic expectation that an analysis of this nature would reveal mechanisms, which is out of line with the state of the field.**  The reviewer objects to the fact that the study does not "reveal the biological mechanisms lead to the detected pattern", and states, "Our contemporary knowledge on forest carbon cycling has moved well beyond using mean climatic variable to extrapolate or guess the response of forest carbon cycling to climate change. The spatial gradient do not necessarily represent the response of forests to climate change." We agree, and fully acknowledge in the paper, that this study does not reveal the biological mechanisms. Further, we do not argue that the spatial gradient represents the response of forests to climate change, as clearly discussed in the final paragraph of the discussion. However, we do argue that broad-scale patterns in C cycling across climatic gradients remain--and should remain--one of several important, complementary approaches to addressing a challenging problem [*sensu* Anderson-Teixeira et al. 2013, GCB]. We note that studies using this approach have been published this year in *Science* [@sullivan_long-term_2020]... **(add some more examples)**. The reviewer's apparent wholesale rejection of this approach seems short-sighted, and the expectation that a single study attempt to explain mechanisms behind global patterns in nine flux variables seems naïve. The implied standard that studies of this type should "reveal the biological mechanisms" could be interpreted in various ways, but the best way of getting at underlying biological mechanisms would be through modeling. Integration of ForC with mechanistic ecosystem models has yet to be acheived, but lies within the vision of leaders in the modeling community, as stated in an opinion piece that I recently reviewed a paper for *GCB* (give citation/ number). (This piece lays out a vision for improvement of community infrastructure for modeling, including one *stated the goal of linking with leading databases, specifically citing ForC*.) In the meantime, the current analysis will be at the clear forefront of studies examinging correlations between forest carbon flux and climate at the global scale.

>>>>

**(1) Reviewer 1 provided an inaccurate assessment of the scope of our analysis relative to previous studies.**  The reviewer states, "...the findings seem not improving contemporary knowledge of forest carbon cycling, and the study appears to be a simple statistical analyses of literature data..." and "the analyses performed were too conventional that similar analyses with a smaller size of similar datasets have been performed a decade ago." These statements betray a lack of perspective on the scope of our analysis relative to previous studies. Whereas most studies consider at most a few flux variables, our considers nine. The most comprehensive similar study is @luyssaert_co_2007, which was published in *GCB* more than a decade ago, includes much less data, does not control for effects of stand age/ disturbance history, and examines latitudinal/ global climatic trends in only 3 variables. This study has been cited >580 times and was highlighted as a noteworthy publication within *GCB* [@long_twentyfive_2020]. It would seem that something along these lines, but with an expanded database and a more carefully controlled treatment of forest age and management/disturbance history, would have high potential to become a "classic" reference in global forest carbon cycling.

@@

**(3) Reviewer 1 set an unrealistic expectation that an analysis of this nature would reveal mechanisms, which is out of line with the state of the field.**  The reviewer objects to the fact that the study does not "reveal the biological mechanisms lead to the detected pattern", and states, "Our contemporary knowledge on forest carbon cycling has moved well beyond using mean climatic variable to extrapolate or guess the response of forest carbon cycling to climate change. The spatial gradient do not necessarily represent the response of forests to climate change." We agree, and fully acknowledge in the paper, that this study does not reveal the biological mechanisms. Further, we do not argue that the spatial gradient represents the response of forests to climate change, as clearly discussed in the final paragraph of the discussion. However, we do argue that broad-scale patterns in C cycling across climatic gradients remain--and should remain--one of several important, complementary approaches to addressing a challenging problem [*sensu* Anderson-Teixeira et al. 2013, GCB]. We note that studies using this approach have been published this year in *Science* [@sullivan_long-term_2020], and recently in *GCB* [@trugman_climate_2019], *JGR* [@li_dissimilatory_2019], and *Scientific Reports* [@chen_spatial_2019]. The reviewer's apparent wholesale rejection of this approach seems short-sighted, and the expectation that a single study attempt to explain mechanisms behind global patterns in nine flux variables seems naïve. The implied standard that studies of this type should "reveal the biological mechanisms" could be interpreted in various ways, but the best way of getting at underlying biological mechanisms would be through modeling. Integration of ForC with mechanistic ecosystem models has yet to be acheived, but lies within the vision of leaders in the modeling community, as stated in an opinion piece that I recently reviewed a paper for *GCB* (give citation/ number). (This piece lays out a vision for improvement of community infrastructure for modeling, including one *stated the goal of linking with leading databases, specifically citing ForC*.) In the meantime, the current analysis will be at the clear forefront of studies examinging correlations between forest carbon flux and climate at the global scale.
